Enhanced Material Point Method to face dynamic problems:\thanks{Funding: This study was funded by Agustín de Betancourt Foundation (grant number 262390106114).}

### 2020-03-11 main.tex
Cambios II 10-3-2020
Cambios 11-3-2020
Cambios II 11-3-2020

% Tikz
\usepackage{stanli}
\usepackage[ugly]{units}

%\usepackage{latexsym}
% etc.
%

@@

\title{Novel improvements in the Material Point Method to face
  dynamic problems: 
  Local-maximum entropy approximation and an explicit   predictor-corrector scheme. \thanks{Funding: This
    study was funded by Agustín de Betancourt Foundation (grant number
    262390106114).}
}
% \subtitle{}

@@

\subsection{Analysis of the Explicit Predictor-Corrector accuracy}
\label{sec:EPC-accuracy}

In this section, the benchmark proposed by Dyka \& Ingel
(1995)\cite{Dyka1995} is considered to illustrate the
capacity of the proposed time integration algorithm to avoid velocity
fields instabilities.

@@

\subsection{Error analysis MPM vs uGIMP vs MPM-\textit{max-ent}}
\label{sec:study-error}

For the convergence analysis, the root-mean-square (RMS) error in the
displacement is computed. RMS error is defined as follows

\begin{equation}
  \label{eq:RMS}
  RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)^2},
\end{equation}

where $\phi_p$ and $\hat{\phi}_p$ are respectively the analytical and
numerical solutions evaluated in the final time step in the position
of each particle.

\begin{figure*}\sidecaption
  \centering
  \resizebox{0.7\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
  }
  \caption{Velocity evolution at the point in the bar left side.}
  \label{fig:Dyka-MPM-uGIMP-LME}
\end{figure*}

\subsection{MPM versus OTM}
\label{sec:mpm-versus-otm}

MPM \cite{Sulsky1994} and OTM
models to avoid tensile instabilities. Here we employ our in-house
codes for both MPM and OTM simulations.

The results are provided for the explicit predictor-corrector version
of the MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM
algorithms. For MPM, piecewise-linear, uGIMP and \textit{max-ent}
basis functions are employed. The OTM algorithm is used only with
\textit{max-ent} shape functions.

>>>>

% Tikz
\usepackage{stanli}
\usepackage[ugly]{units}
% \usetikzlibrary{decorations}
% \usetikzlibrary{arrows}
\usetikzlibrary{plotmarks}

%\usepackage{latexsym}
% etc.

%

@@

% \title{Novel improvements in the Material Point Method to face
%   dynamic problems: 
%   Local-maximum entropy approximation and an explicit predictor-corrector scheme. \thanks{Funding: This
%     study was funded by Agustín de Betancourt Foundation (grant number
%     262390106114).}
% }

\title{Enhanced Material Point Method to face
  dynamic problems:\thanks{Funding: This
    study was funded by Agustín de Betancourt Foundation (grant number
    262390106114).}
}
\subtitle{Local-maximum entropy approximation and an explicit
  predictor-corrector scheme}

@@

% \subsection{Error analysis MPM vs uGIMP vs MPM-\textit{max-ent}}
% \label{sec:study-error}

% For the convergence analysis, the root-mean-square (RMS) error in the
% displacement is computed. RMS error is defined as follows

% \begin{equation}
%   \label{eq:RMS}
%   RMS = \sqrt{\frac{1}{N} \sum^{N}_p \left( \phi_p - \hat{\phi}_p \right)^2},
% \end{equation}

% where $\phi_p$ and $\hat{\phi}_p$ are respectively the analytical and
% numerical solutions evaluated in the final time step in the position
% of each particle.

\section{Analysis of the proposed improvements.}
\label{sec:Analysis-proposed-improvements.}

This section is devoted to test the ability of both predictor-corrector
time integration scheme and the local \textit{max-ent} approximants to
overcome spurious oscillations due to the grid crossing and high
frequency loads under the context of the MPM.

\subsection{Dyka bar}
\label{sec:dyka-bar}

High frequency , the benchmark proposed by Dyka \& Ingel
(1995)\cite{Dyka1995} is considered to illustrate the
capacity of the proposed time integration algorithm to avoid velocity
fields instabilities.

@@

\subsection{Andersen block}
\label{sec:andersen-block}

In order to test the ability of this interpolation technique to deal
with grid crossing instabilities, we will simulate the compression of
a linear elastic soft soil due to the gravity force, \ref{fig:block}.

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \input{Figures/Block.tex}}
  \caption{Geometrical description of a soil block }.}
  \label{fig:block}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/FE_vs_PCE_CFL_05}
  }
  \caption{Geometrical description of a soil block.}
  \label{fig:block-MPM}
\end{figure}

\begin{figure}\sidecaption
  \centering
  \resizebox{\hsize}{!}{
    \includegraphics[width=\textwidth]{./Figures/Block_CFL_01_MPM.png}
  }
  \caption{Geometrical description of a soil block }.}
\label{fig:block-MPM}
\end{figure}

% \subsection{MPM versus OTM}
% \label{sec:mpm-versus-otm}

% MPM \cite{Sulsky1994} and OTM
% models to avoid tensile instabilities. Here we employ our in-house
% codes for both MPM and OTM simulations.

% The results are provided for the explicit predictor-corrector version
% of the MPM scheme (Algorithm \ref{alg:PCE-algorithm}) and OTM
% algorithms. For MPM, piecewise-linear, uGIMP and \textit{max-ent}
% basis functions are employed. The OTM algorithm is used only with
% \textit{max-ent} shape functions.

% \begin{figure*}\sidecaption
%   \centering
%   \resizebox{0.7\hsize}{!}{
%     \includegraphics[width=\textwidth]{./Figures/Velocity-Comparative}
%   }
%   \caption{Velocity evolution at the point in the bar left side.}
%   \label{fig:Dyka-MPM-uGIMP-LME}
% \end{figure*}
